---
title: "Transfer Learning on Stack Exchange Tags"
output: html_notebook
---

The main goal of this competition is to predict stack exchange tags of many topic based on <b> Transfer Learning approach</b>. I will try many NLP approach and many supervised and unspervised learning approach. I will use `sparklyr` R Spark interface. I'm not a Machine Learning expert but i'm going to explore many approach to solve this problem ! 

### Import necessary library
```{r}
library(sparklyr)
library(dplyr)
library(ggplot2)
library(plotly)
library(stringr)
library(plotly)
library(tm)
library(wordcloud)
```
Lets now upload the differents dataframe data, we have 6 topic category in addition to the test data and the submission example : 

```{r}
biology =  read.csv("../biology.csv")
travel = read.csv("../travel.csv")
robotic = read.csv("../robotics.csv")
cooking = read.csv("../cooking.csv")
crypto = read.csv("../crypto.csv")
diy = read.csv("../diy.csv")
test = read.csv("../test.csv")
sample_submission = read.csv("../sample_submission.csv")
```


### Functions

`countDistinctTags(df,nFreq)` show the most frequent `nFreq` tags on the dataframe `df` passed on parameter, we plot a bar chart and word cloud based on tags.

```{r}
countDistinctTags <- function(df,nFreq){
  df <- as.data.frame(as.factor(unlist(str_split(df$tags," "))))
  colnames(df) <- c("tags")
  df <- data.frame(table(df$tags))
  colnames(df) <- c("tags","Freq")
  df <- df[order(df$Freq,decreasing = TRUE),]
  df <- df[1:nFreq,]
  p <- plot_ly(x = df$tags, y = df$Freq,type="bar") %>%
    layout(yaxis = list(title = "Freq"),xaxis = list(title = "Tags"))
  return(p)
}

tst <- countDistinctTags(travel,40)
tst
```


